Frame Competition

### 2022-07-12 pres/Presentation.Rmd
Update image
start presentation

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#004A95", background_color = "#bfbfbf",
  base_font_size = "32px",
  header_h1_font_size = "1.3rem",
  header_h2_font_size = "1.2rem",
  header_h3_font_size = "1.05rem",
  footnote_font_size = "0.75rem",
  header_font_google = google_font("Lato", '700'),
  text_font_google   = google_font("Lato", "400"),
  code_font_google   = google_font("Fira Mono")
)

@@

```{r vectors, fig.cap="Schematic representation of topic vectors for party communication and news articles."}

data.frame(
  item = c("News Article", "Party A", "Party B",
            "News Article", "Party A", "Party B"),
  dim1 = c(0,  0.2, 0.8,
            0,0,0),
  dim2 = c(1, 0.8, 0.2,
            0,0,0)
) %>% 
ggplot(aes(x = dim1, y = dim2, 
        color = item, linetype = item)) +
  geom_line() +
  geom_point(alpha = 0.3) + 
  theme_minimal() +
  xlab("Attention to Consideration 1") +
  ylab("Attention to Consideration 2") +
  theme(legend.title = element_blank())

@@

>>>>

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#004A95", background_color = "#bfbfbf",
  base_font_size = "40px",
  header_h1_font_size = "1.3rem",
  header_h2_font_size = "1.2rem",
  header_h3_font_size = "1rem",
  footnote_font_size = "0.75rem",
  header_font_google = google_font("Lato", '700'),
  text_font_google   = google_font("Lato", "400"),
  code_font_google   = google_font("Fira Mono")
)

@@

class: inverse, center, middle

# Frame Competition

#### Nicolai Berk<sup>*</sup>

Presentation prepared for the first OX|BER Graduate Workshop

Berlin, 14th of July

.left[.footnote[<sup>*</sup> Dynamics RTG & Humboldt Universität Berlin]]

---

## Motivation: Issue Ownership

```{r MPAtt}

fread("https://www.dropbox.com/s/3taauo34rumthtm/final_dataset.csv?dl=1") %>% 
  mutate(date = as.Date(date, format = "%d/%m/%Y"),
         month = lubridate::floor_date(date, "quarter")) %>% 
  filter(date >= as.Date("2013-01-01")) %>% 
  group_by(month, sender) %>% 
  summarise(imm_att = mean(coding)) %>% 
  ggplot(aes(month, imm_att, fill = sender)) +
  geom_col(position = "dodge2") + 
  theme_minimal() +
  ggtitle("Attention to migration in mainstream parties' press releases", "2013-2019") +
  scale_fill_manual(values = c("#000000", "#e3000f")) +
  theme_xaringan() +
  ylab("") + xlab("")

@@

---

## Motivation II

- Parties only option to **remain mute** on other parties' issues?
- Framing literature suggests that issue definitions affect voters' policy preferences.
- Some experimental literature that this can affect issue ownership [@Seeberg2019].

--

### But can framing affect voting behaviour?

---

## Argument

1. Issue framing affects issue preferences.
2. Dominant framing of an issue changes public opinion on that issue.
3. Public votes based on proximity to parties' issue positions.

### Issues more or less beneficial dependent on *dominant framing*!

---

class: center, inverse, middle

# Research Design

---

---

## Measuring Frame Dominance

```{r vectors}

data.frame(
  item = c("News Article", "Party A", "Party B",
            "News Article", "Party A", "Party B"),
  dim1 = c(0,  0.2, 0.8,
            0,0,0),
  dim2 = c(1, 0.8, 0.2,
            0,0,0)
) %>% 
ggplot(aes(x = dim1, y = dim2, 
        color = item, linetype = item)) +
  geom_line(size = 2) +
  geom_point(alpha = 0.3, size = 4) + 
  theme_minimal() +
  xlab("Attention to Consideration 1") +
  ylab("Attention to Consideration 2") +
  theme(legend.title = element_blank()) +
  theme_xaringan()
